Distributions

### 2021-12-16 Ch2_distributions/Ch2_Figures.Rmd
Progress.
almost done with figures for step length models.

```{r fig.height=6}

cp.bic %>% 
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
  ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
  #geom_col() +
  geom_point() +
  scale_color_manual(values = cols.fig2) +
  theme_classic() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  labs(y = "Bootstrap replicates", x = "") +
  theme(legend.position = "none") -> Fig4a

pp.bic %>% 
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
  ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
  #geom_col() +
  geom_point() +
  scale_color_manual(values = cols.fig2) +
  theme_classic() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  labs(y = "Bootstrap replicates", x = "") +
  theme(legend.position = "none") -> Fig4b

np.bic %>% 
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
  ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
  #geom_col() +
  geom_point() +
  scale_color_manual(values = cols.fig2) +
  theme_classic() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  labs(y = "Bootstrap replicates", x = "BIC units from best model") -> Fig4c

@@

# Visualize them as density curves:

>>>>

```{r fig.height=4}

cp.bic %>% 
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
  ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
  #geom_col() +
  geom_point(alpha = 0.8, shape = 15) +
  scale_color_manual(values = cols.fig2) +
  theme_classic() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  labs(y = "Bootstrap \n replicates", x = "") +
  theme(legend.position = "none") -> Fig4a

pp.bic %>% 
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
  ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
  #geom_col() +
  geom_point(alpha = 0.8, shape = 15) +
  scale_color_manual(values = cols.fig2) +
  theme_classic() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  labs(y = "Bootstrap \n replicates", x = "") +
  theme(legend.position = "none") -> Fig4b

np.bic %>% 
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
  ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
  #geom_col() +
  geom_point(alpha = 0.8, shape = 15) +
  scale_color_manual(values = cols.fig2) +
  theme_classic() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  labs(y = "Bootstrap \n replicates", x = "BIC units from best model") -> Fig4c

@@
